\section{Risks}
\label{sec:dp-tpcelec-risks}

\fixme{new standard risks table for autogenerating latex as of 3/25. I will send email. Anne}

\begin{dunetable}
[TPC Electronics System Risk Summary]
{p{0.15\textwidth}p{0.75\textwidth}}
{tab:dp-tpcelec-risks}
{TPC Electronics System Risk Summary.}
ID & Risk \\ \toprowrule
1 & Obsolescence of electronic components over the period of the experiment \\ \colhline
2 & Modification to \dword{fe} electronics due to evolution in design of \dwords{pd} \\ \colhline
3 & Damage to electronics due to \dword{hv} discharges or other causes \\ \colhline
4 & Problems with \dword{fe} card extraction due to insufficient clearance \\ \colhline
5 & Overpressure in the \dwords{sftchimney} \\ \colhline
6 & Leak of nitrogen inside the \dword{dpmod} via cold flange \\ \colhline
7 & Data flow increase due to inefficient compression caused by higher noise \\ \colhline
8 & Damage to \dword{utca} crates due to presence of water on the roof of the cryostat \\ \colhline
9 & Clogging ventilation system of \dword{utca} crates due to bad air quality \\ \colhline
\end{dunetable}

The design of the \dual electronics system takes into account several risks, % factors, 
summarized in Table~\ref{tab:dp-tpcelec-risks}. While the actual design was completed in 2016, the production for %\dword{dune} is foreseen 
the \dword{dpmod} is expected to start as early as 2022. In the interim, %this period, the team from 
the \dword{dp} \dword{tpc} electronics consortium team that %, which 
performed the original R\&D for the electronics design %since from 2006 until 2016, 
will continuously monitor the market to ensure that all single component parts needed to assemble the electronics cards remain in stock on %a timescale of the 
the timescale required for production of the cards for \dword{dune}. Any elements identified as at risk will be replaced in the executive design with functionally equivalent parts. While this may necessitate some minor design adaptations (e.g., modifying the PCB layout to accommodate a different component footprint), the overall functionality of the system will remain unchanged. An industry survey will also be undertaken for the \dword{fe} \dword{asic} manufacturing process, such that, if a real risk is identified, the \dword{asic} production can be re-qualified for a different production process. The long-term component obsolescence (Risk 1) %of 
over the lifetime of the experiment ($>$ \num{20} years) will be mitigated by procuring an adequate number of spares at the time of %the 
production.

A strict and timely %follow-up 
reassessment of the \dword{fe} requirements %from in an event of any possible 
necessitated by an evolution of the \dual \dword{pds} should allow us to %address any potential modification of 
modify the \dword{lro} \dword{fe} electronics design accordingly (Risk 2). % to be addressed (ID 2).

We believe that the \dword{fe} cards %should 
have suitable protection to prevent damage caused by \dword{crp} discharges (Risk 3) since the  TVS diodes %used in the current design 
have provided sufficient protection %for the \dword{fe} electronics 
in \dword{wa105}. By design, the \dword{fe} cards remain accessible and could be replaced.
However, the \dwords{sftchimney} require sufficient overhead clearance (Risk 4) to extract and re-insert %so that 
the blades holding the \dword{fe} cards. % can be extracted and re-inserted. 
This %should be 
is addressed by imposing a clearance %an appropriate 
requirement on %for 
\dword{lbnf}.

The \dwords{sftchimney} are equipped with safety valves that vent excess gas if pressure suddenly rises (Risk 5). The over-pressure threshold must be set low enough that the flanges suffer no significant damage. The pressure of the nitrogen inside the \dwords{sftchimney} must %should 
be monitored to detect potential leaks. In the event of a leak %towards the inner volume of the \dword{dpmod} 
via the cold flange (Risk 6), the chimney volume will %should 
be filled with argon gas to mitigate the risk of %effect 
nitrogen contamination %carries for 
quenching the scintillation light.  

To ensure the continuous flow of digitized data to the \dword{daq} (Risk 7), the data rate must stay below the \dword{mch} bandwidth.  %, which 
%is a potential risk if the 
In the event data compression becomes less efficient because of higher noise, this bandwidth could be exceeded. To mitigate this risk, we currently have a %margin (a 
factor of \num{5} margin in the available bandwidth: \SI{10}{Gbit/s} \dword{mch} compared to the expected rate of \SI{1.8}{Gbit/s} (Table~\ref{tab:dp-utcabandwidth}).

%Potential damage to the \dword{utca} crates due to water condensation on the roof of the cryostat (Risk 8) or poor air quality (Risk 9)should be mitigated by the \dword{lbnf} requirements that the top of the cryostat remain dry and the air quality similar to any industrial environment (e.g., at CERN or \dword{fermilab}). Large quantities of dust in the detector caverns at SURF should be avoided after the \dword{utca} crates are deployed.
\dword{lbnf} requirements that the top of the cryostat remain dry and the air quality remain comparable to a standard industrial environment (e.g., at \dword{cern} or \dword{fermilab}) mitigate the risk of potential damage to the \dword{utca} crates from water condensation (Risk 8) or poor air quality (Risk 9). It is essential to avoid large quantities of dust in the detector caverns at \dword{surf} after the \dword{utca} crates are deployed.
