\section{Interfaces}
\label{sec:dp-pds-interfaces}

The \dword{pds} has several interfaces with other subsystems and the global \dword{dune} systems. The interface documents related to \dword{dp} \dword{pds} are given in Table~\ref{tab:dppd_t_8}. Only some of the basic interfaces are summarized below. 

\begin{dunetable}
[\dual \dword{pd} interface documents]
%{|l|c| p{0.8\textwidth}}
{p{0.25\textwidth}p{0.5\textwidth}l}
{tab:dppd_t_8}
{\dual \dword{pd} interface documents}

%\dual \dword{pd} Interface Document & DUNE docdb number \\ \toprowrule
Interfacing System & Description & Linked Reference \\ \toprowrule
\dword{dp} electronics & Electronics racks, connectors & \citedocdb{6772} \\
\dword{dp} \dword{hv} & \dword{fc}, cathode, \dword{gg} and \dword{pds} installation sequence, possibility of individual \dwords{gg} on the \dword{pmt} support structures, possibility of reflective wavelength shifting foils on the inner surface of the \dword{fc}   & \citedocdb{6799} \\
\dword{daq} & Data format, trigger distribution & \citedocdb{6802} \\
%\dword{cisc} & 6781 \\
\dshort{cisc} & Layout of cryogenic instrumentation, slow control of the \dword{pds} power supplies and calibration system & \citedocdb{6781} \\ %capitalize first letter dword workaround
\dune Physics & Physics requirements & \citedocdb{7087} \\
Software and Computing & Development of simulation, reconstruction and analysis tools & \citedocdb{7114} \\
Calibration & Global monitoring of \dword{pds} \dwords{pmt} & \citedocdb{7060} \\
%\dword{itf} & 7033 \\
\dword{itf} & Shipping and receiving of the \dword{pds} components, \dword{tpb} coating of the \dwords{pmt} & \citedocdb{7033}\\
Detector and Facilities Infrastructure & \dword{pmt} supporting bases, cable trays, feedthrough flanges, access to conventional facilities, participation in the \dword{dss} & \citedocdb{6979} \\
\dshort{uit} & Transportation of the \dword{pds} components to and between underground areas, clean room activities, storage and installation & \citedocdb{7006} \\
\end{dunetable}

%\fixme{Update to standard table format for interface document tables, Sec.~3.5.2 in \url{https://dune.bnl.gov/docs/guidance.pdf}.}

\begin{itemize}

\item \dword{dp} Electronics: The \dword{pds} shares the same \dword{fe} electronics standard as the charge readout, which is \dword{utca}-based \cite{utca}. The \dword{dp} electronics will provide data in continuous streaming (\num{12} bits at \SI{2.5}{\MHz} sampling) of all \dword{pds} channels over the \SI{10}{\Gbps} links. The number of photomultipliers to be read out is \dpnumpmtch to be distributed among \num{60} AMC cards (\num{20} \dword{utca} crates for the \num{20} \dword{pds} sectors, \num{36} readout channels in \num{3} AMC cards/crate). Readout racks for the sectors will be \SI{6}{\m} apart along the \SI{60}{\m} side, and on both sides. Deeper understanding of \dword{pmt} characteristic (saturation, recovery time, ringing, pre-and after pulsing, etc.) will be provided by \dword{dp} \dword{pds}. The type of the connectors to be used at the FE input panel will be determined by the \dword{dp} Electronics Consortium and will be implemented by \dword{dp} \dword{pds}.

\item \dword{hv}: This interface includes the consideration of the distance between the cathode/ground grid and the \dword{pmt} planes, the possible implementation of the ground grid at the individual \dword{pmt} level, and the possible implementation of the wavelength shifting films on the inner surface of the field cage. The \dword{hv} consortium will also be the primary group that the \dword{pds} consortium will be communicating in order to harmonize the underground installation.

\item \dword{daq}: The hardware interface is mainly through optical fibers. \dword{dp} \dword{pds} provides trigger and data in continuous streaming;  the interface also includes the \dword{daq} software.

\item \dshort{cisc}: The main interface points with the \dword{cisc} are the layout of the cryogenic instrumentation (e.g., purity monitors and light emitting system for the cameras) and the \dword{pmt} support structures and cabling; and the slow control of the \dword{pds} power supplies and calibration system. The \dword{pds} \dwords{pmt} are part of \num{20} sectors with \num{36} \dwords{pmt} each, and will be controlled with \num{20} \dword{hv} crates.

\item \dune Physics: \dual \dword{pd} has interfaces with the overall physics requirements on energy and time together with classification of events, decay modes and neutrino flavors.

\item Software and Computing: This interface is on the development of simulation, reconstruction and analysis tools.

\item Calibration: The \dword{pds} is participating in the \dword{dune} global calibration task force and will provide handles to allow global monitoring of the \dword{pmt} performance.

\item \dword{itf}: The operations at the \dword{itf} are described in Section~\ref{subsec:dp-pds-itf}. The interface items can be summarized as shipping and receiving of the \dword{pds} components, \dword{tpb} coating of the \dword{pmt} windows, basic functionality testing, repairing and repackaging at the facility. The interface includes recycling and returning the packaging materials.

\item Detector and Facilities (\dword{lbnf}) Infrastructure: The \dword{pds}
\dword{pmt} supporting base on the cryostat floor; cold cables together with the cable trays, and the feedthroughs are the major interfaces with the facility. The cables and calibration fibers are routed in cable trays from the ceiling \fdth flanges to the bottom of the cryostat. The installation of the \dwords{pmt} and the connection of the fibers and \dword{hv}/signal cables to the \dwords{pmt} are under the responsibility of \dword{pds}. Other interfaces with the facility include access to conventional facilities and participation in the detector safety systems. 

\item \dshort{uit}: This interface with the \dword{uit} includes the transportation of the \dword{pds} components to and between underground areas, clean room activities and storage, and installation coordination with the other teams. The details are described in Section~\ref{subsec:dp-pds-undergroundinstallation}.

\end{itemize}

