%\section{Installation, Integration, and Commissioning}
%\label{sec:sp-calib-iic}

%\fixme{This is a copy of text we sent to Jim Stewart for the integration chapter. We need guidance for how this chapter and that chapter need to reference each other.}
% Text from here: https://docs.google.com/document/d/1-rqOJOFtTlNPj1myXHtz3eNL75u1iZE5yfizwMTFsu4/edit

%\fixme{SG: I am done reviewing and did restructing; KM: Only one comment below to remove a sentence. JM: check if you are okay, more details sent in email.}

\fixme{The heading in the PDF needs a comma after "Integration".}

This section describes the installation plans and requirements for calibration systems. For all calibration subsystems, space on the mezzanine and on top of the cryostat surrounding each calibration port is important for powering and operating the calibration systems. The subsystems can be installed once the associated components are installed in the cryostat (e.g., for the laser after the periscopes are installed). All subsystems will be installed using only the cryostat roof ports other than some laser system components.

\subsubsection{Ionization Laser System} 
%Only the laser system (alternative design) has components that must be installed inside the cryostat through the \dword{tco}. The pulsed neutron source and radioactive source deployment systems are installed using only the cryostat roof ports.

%\fixme{To be consistent with the rest of the manuscript, the following italicized headings should instead be bolded: Inside TCO, Outside TCO.}

%{\bf Inside \dword{tco}:} A long horizontal track system will be installed outside the end-wall \dword{fc}, directly below the corresponding calibration ports and suspended by them. The system farthest away from the \dword{tco} must be installed before \dword{tpc} (\dword{fc}/\dword{apa}/\dword{cpa}) installation begins. This requires simultaneous installation of the corresponding periscopes from the calibration ports, so the two systems can be properly connected. The relevant \dword{qc} is essentially an alignment test.

%In addition, the laser positioning system has sets of photo-diodes that can either be pre-mounted on the \dword{hv} system bottom ground plane or simply placed on a tray close to the cryostat membrane. The only step that must be done inside the \dword{tco} is connecting the cabling to available flange (work is still underway to decide how to route cables and which flanges to use).

Aligning the visible and UV (Class 4) lasers requires special safety precautions and must be carried out once for each periscope/laser system before installing further \dword{tpc} components. For that reason, the laser boxes must be installed on the cryostat roof as soon as the top area of the cryostat becomes accessible. 

The periscopes on top of the \dword{tpc} can be installed after the relevant structural elements, especially the \dword{fc} and \dword{crp} modules, are installed. Installation should proceed in sequence with the assembly of other components, with the furthest from \dword{tco} assembled first. The laser positioning system (LPS) \fixme{This abbreviation is not in the glossary. Should it be added?} can be used to align the periscopes as they are installed, so the LPS must also installed in the same sequence as the periscopes. %\fixme{Please check the previous sentence for accuracy. It was not clear if the reference in the sentence was to periscopes or \dword{tpc} components.}

In addition, the laser positioning system has sets of photo-diodes \fixme{I cannot recall if "photo-diodes" has been hyphenated in previous chapters/volumes.} that can be
%either be pre-mounted on the \dword{hv} system 
%bottom ground plane 
%or simply 
placed on a support bracket close to the cryostat membrane below the ground grid. The only other step that must be done inside the cryostat
%\dword{tco} 
is connecting the cabling to the available flange (work is still underway to decide how to route cables and which flanges to use).

%\fixme{KM: not confident in this sentence} It may be possible to do this special alignment operation for all lasers at roughly the same time, to minimize any possible disruptions. 

%%JM. Commented out next sentence. It is SP-specific. Not sure where are the support structures for DP and if they would block us.
%A support beam structure closest to the \dword{tco} temporarily blocks the calibration ports, but it is removed after the last \dword{tpc} component is installed. After that, the final calibration components can be installed, including the periscopes on the \dword{tco} end wall. 
%The horizontal track closest to the \dword{tco} would be the last item to be installed. 

\subsubsection{Laser Positioning System}
The laser positioning system has several parts that must be installed inside the 
cryostat,
%\dword{tco} 
and some of them must be integrated with the 
\dword{hv} system during installation underground. 
%Two components, baseline design: mirror clusters and alternative design: diodes, require an interface with the \dword{hv} and \dword{fc} structural systems.

The pin-diode \fixme{Again, I recall seeing pin-diode before, but I cannot recall if it was hyphenated.} system, that follows the mini-\dword{captain} experience, uses a set of diodes that fire when the laser beam hits them. Because the laser shoots from above and the diodes must be in a low voltage region, the plan is to place the diodes below the bottom ground grid, facing upward. They can be pre-mounted on a support bracket close to the cryostat membrane. 
%either be pre-mounted on the \dword{hv} system 
%bottom ground plane or simply on a support bracket
%tray 
%close to the cryostat membrane.

For the pointing measurement, the beams will pass through the cathode and ground grid electrodes and hit the diodes below. At least \num{20} of these diode clusters would be installed, and assembly must be done underground at the \dword{hv} assembly point.
%in case the ground planes are used.


The second laser positioning system consists of a set of about \num{30} mirror clusters: a plastic piece holding four to six small mirrors \SI{5}{\mm} in diameter, each at a different angle; the ionization laser will point to these mirrors to obtain an absolute pointing reference. These clusters will be attached to the wall \dword{fc} profiles facing into the \dword{tpc}. 
%These cross bars must contain small alignment slots, matching the cluster pieces, in order for us to know the exact position of each cluster. 
This attachment/assembly of the mirror clusters on corresponding \dword{fc} profiles will be done during \dword{fc} assembly underground.

\subsubsection{Photoelectron Laser System} 
A large number of photoelectric targets (about \num{4000}) must be fixed to the cathode grid. Experience from other experiments indicates that targets can be glued to the cathode surface; this
%can be done after cathode assembly but 
must be done before the cathode is installed in the cryostat. 

Once the 
%\dwords{cpa} are 
cathode grid is in place, the photoelectric target locations will need a high precision survey, which is necessary for the absolute calibration of the electric field with the photoelectron laser. 

The third part of the installation is placing quartz optical fibers close to the \dword{crp}, which are
%anode plane, 
needed to illuminate the photoelectric targets with Nd:Yag\footnote{Nd:YAG stands for neodymium-doped yttrium aluminum garnet; Nd:Y$_{3}$Al$_{5}$O$_{12}$) is a crystal that is used as a lasing medium for solid-state lasers.} laser. 
%\fixme{I do not know if this requires a definition or not. It is not in either the common glossary or the manuscript glossary. SG:done; added as a footnote; glossary not needed since it only appears like twice in the document} laser light. 
Fiber tips must be properly fastened and oriented for effective illumination, and fiber bundle routing will bring the fiber bundles to the outside of the cryostat where Nd:Yag laser injection points will be located. 
%\todo{SG: need text for this.}

\subsubsection{Pulsed Neutron Source System} 
The \dword{pns} will be installed after the human access ports are closed because the source sits above the cryostat. Installing the system should take place in two stages. In the first stage, the assembly of the system would be independent of the \dword{tpc} installation. The whole system will be installed on the ground outside the cryostat at a dedicated radiation safe facility. Once assembled, the neutron source will be lifted by crane and integrated with the cryostat structure. Final \dword{qc} testing for the system will involve operating the source and measuring the flux with an integrated monitor and dosimeter.



\begin{comment}
\subsection{Installation}
Only the laser system alternative design has components that need to installed inside the cryostat via the \dword{tco}. The pulsed neutron source and radioactive source deployment systems are installed only using the cryostat roof ports.

Laser, inside \dword{tco}: Installation of the periscopes from the top of the cryostat roof does not require any system elements fixed to either the \dword{hv} or \dword{crp}. However, an operator should be present within the cryostat to check for interferences while lowering the periscopes.  
%A long horizontal track system is to be installed outside the end-wall field cage, directly below the corresponding calibration ports, and suspended by them. The system farthest away from the \dword{tco} must be installed before \dword{tpc} (\dword{fc}/\dword{apa}/\dword{cpa}) installation begins. This installation requires the simultaneous installation of the corresponding periscopes, from the calibration ports, so that the two systems can be properly connected. The relevant QC is essentially alignment test.

In addition, the alternative laser positioning system has sets of photo-diodes pre-mounted on the \dword{hv} system bottom ground planes. The only step that needs to be done inside the \dword{tco} is connecting the cabling to available flange (still working out how to route cables and which flange to use).



Laser, outside \dword{tco}: The periscopes on the top of the \dword{tpc} in the center can be installed after the relevant structural elements (e.g. field cage), these proceed in sequence with the assembly of other components (furthest from \dword{tco} is assembled first) and alignments can be done as elements are installed with the alignment laser system. Once for each periscope/laser system, prior to the installation of further \dword{tpc} components, we will need to clear the cavern to align the UV (Class 4) and visible lasers this will need special safety precautions. It may be possible to do this special alignment operation for all lasers at roughly the same time, to minimize the disruption.  

A support beam structure closest to the \dword{tco} temporarily blocks the calibration ports, this is removed after the last \dword{tpc} component. After that, the final calibration components can be installed, including the the periscopes on the \dword{tco} endwall and the horizontal track closest to the \dword{tco} would be the last items to be installed. 



Power supply and racks:  Space on mezzanine close to each calibration port is important in order to power and operate the calibration systems (laser and \dword{pns}). They can be installed following the associated periscope installation.

Radioactive Source Deployment System: The \dword{rsds} guide system can be installed as the first element before \dword{tpc} elements for the endwall furthest from the \dword{tco}, and the last system (concurrent and coordinated with the alternative laser system).
The \dword{rsds} is installed at the top of the cryostat and can be installed when DUNE is working.
\end{comment}

%\subsection{Commissioning}

%Once the detector is completely full, the laser system and pulsed neutron source can be tested.
