\section{Sensitivity Methods}
%{\it Assigned to:} {\bf Elizabeth Worcester} with contributions from Chris Backhouse and Callum Wilkinson. 
\label{sec:physics-lbnosc-sens}


 %Method for calculation of sensitivity should be described. Describe previous work with Globes which might include validation of new software framework. Describe CafAna and any specifics of the DUNE fits. 

%\begin{itemize}
%\item Sensitivity Calculation Methods - Text from CDR
%\item Statistical Methods - Text from CDR 
%\item GLoBES -  EW
%\item CAFAna Methods - CB
%\item Dune fit - CW
%\end{itemize}

Sensitivities to the neutrino mass ordering, \dword{cpv}, and $\theta_{23}$ octant, as well as expected resolution for neutrino oscillation parameter measurements, are obtained by simultaneously fitting the \numutonumu, $\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu$, \numutonue, and $\bar{\nu}_\mu \rightarrow \bar{\nu}_e$ far detector spectra along with selected samples from the near detector.  It is assumed that 50\% of the total exposure is in neutrino beam mode and 50\% in antineutrino beam mode.  A 50\%/50\% ratio of neutrino to antineutrino data has been shown to produce a nearly optimal sensitivity, and small deviations from this (e.g., 40\%/60\%, 60\%/40\%) produce negligible changes in the sensitivity. %\todo{check this is still the case} 

Within all fits, neutrino oscillation parameters are all allowed to vary, constrained by a Gaussian prior with 1$\sigma$ width as given by the relative uncertainties shown in Table~\ref{tab:oscpar_nufit}. Systematic uncertainty constraints from the near detector are included either by explicit inclusion of near detector samples within the fit or by applying constraints expected from the near detector data to \dword{fd}-only fits.

In the sensitivity fits, experimental sensitivity is quantified using a test statistic, $\Delta\chi^2$, which is calculated by comparing the predicted spectra for alternate hypotheses.  The details of these fits are described in Section~\ref{sect:methods-dunefits}. 
A ``typical experiment'' is defined as one with the most probable data given a set of input parameters, i.e., in which no statistical fluctuations have been applied. In this case, the predicted spectra and the true spectra are identical; for the example of \dword{cpv}, $\chi^2_{\mdeltacp^{true}}$ is identically zero and the $\Delta\chi^2_{CP}$ value for a typical experiment is given by $\chi^2_{\mdeltacp^{test}}$. The interpretation of $\sqrt{\Delta\chi^2}$ has been discussed in \cite{Qian:2012zn,Blennow:2013oma}; it may be interpreted as approximately equivalent to significance in $\sigma$. 

\dword{dune} sensitivity has been studied using several different fitting frameworks. GLoBES (General Long Baseline Experiment Simulator)\cite{Huber:2004ka,Huber:2007ji} %facilitates the use of standardized input formats to calculate predicted spectra and defines methods that enable a test statistic to be computed given a set of inputs. The details of DUNE's GLoBES implementation have been described in \cite{Acciarri:2015uup,Alion:2016uaj,Bass:2014vta}. GLoBES
-based fits have been used extensively in the past, in particular for sensitivity studies presented in the \dword{dune} \dword{cdr}; details are available in \cite{Acciarri:2015uup,Alion:2016uaj,Bass:2014vta}. \dword{globes} is now used primarily for quick studies in support of algorithm development and optimization. \dword{valor}\cite{valorweb} has also been used for internal studies. \dword{cafana}, described in Section~\ref{sect:methods-cafana}, was initially developed within the \dword{nova} collaboration and is the primary fitting framework for \dword{dune}. Unless otherwise noted, fits presented in this document are performed within \dword{cafana}. Section~\ref{sect:methods-dunefits} describes the detailed implementation of \dword{dune} fits within the \dword{cafana} fitting framework.

%\subsection{GLoBES}
%\label{sect:methods-globes}
% 
%The expected event rates as a function of reconstructed energy are computed from inputs of flux, oscillation parameters, cross-sections, detector energy response matrices, and detector efficiency. Specifically, the event spectra are calculated to be
%\begin{equation}
%    N_i^{c_{\beta}}(\theta) = \sum_j^{N_{E_{true}}} n_j^{c_{\alpha}} \cdot P_j^{c_{\alpha} \rightarrow c_{\beta}}(\theta) \cdot S_{ij}^{c_{\beta}}
%\end{equation}
%
%where $c_{\alpha}$ represents the channel being considered before oscillation, $c_{\beta}$ represents the channel being considered after oscillation, the subscript $i$ represents a reconstructed energy bin, the subscript $j$ represents a true energy bin, $n_j^{c_{\alpha}}$ is the expected interaction rate in the far detector for the unoscillated channel $c_{\alpha}$ and includes the neutrino flux, interaction cross-section, and detector efficiency inputs, $P_j^{c_{\alpha} \rightarrow c_{\beta}}(\theta)$ is the probability for oscillation $c_{\alpha} \rightarrow c_{\beta}$ and is a function of the oscillation parameters, true neutrino energy, baseline, and matter density, and $S_{ij}^{c_{\beta}}$ is a matrix that defines the response of the detector by mapping the true neutrino energy to a PDF of reconstructed neutrino energy \fixme{cite M. Bass thesis}. 
%
%The GLoBES analyses in DUNE make use of built-in $\chi^2$ definitions which may be minimized and compared to each other to form the test statistics described above. This quantity is calculated to be
%\begin{equation}
%    \Delta\chi^2 = 2 \sum_i^N [N_i^{exp}(\theta,f) - N_i^{true} + N_i^{true}ln[\frac{N_i^{true}}{N_i^{exp}(\theta,f)}] + \sum_j^{N_{systs}}\frac{f_j^2}{\sigma_{f_j}^2} + \sum_k^{N_{osc}}\frac{(\theta_k^{nominal}-\theta_k)^2}{\sigma_{\theta_k}^2}]
%\end{equation}
%and is minimized with respect to all free parameters, including oscillation parameters that are not fixed and normalization uncertainties that are applied to signal and background to approximate the expected effects of systematic uncertainty. 
%
%The flux inputs to GLoBES are the result of a GEANT4 simulation and are identical to the flux input to the full Monte Carlo simulation described below. The cross-sections are produced by GENIE 2.4.8\cite{Andreopoulos:2009rq}. The detector response and efficiency are produced by analysis of simulation outputs. In the case of the sensitivity presented in the DUNE CDR, this was a parameterized "Fast MC" simulation. Presently, the results of full MC simulation and analysis are used to produce GLoBES inputs, such that only these details are changed relative to the CDR and the resulting sensitivity calculations may be compared directly to previous DUNE results. While these studies have aided development of the analysis algorithms presented in this document, GLoBES-based sensitivity analyses have been superceded by the CAFAna-based analysis described in the following section.

\subsection{The Analysis Framework}
\label{sect:methods-cafana}

To demonstrate the sensitivity reach of \dword{dune}, we have adopted the analysis framework known as \dword{cafana}. This framework was initially developed for the \dword{nova} experiment and has been used for $\nu_\mu$-disappearance, $\nu_e$-appearance, and joint fits, plus sterile neutrino searches and cross-section analyses.

In the sensitivity studies, the compatibility of a particular oscillation hypothesis with the data is evaluated using the likelihood appropriate for poisson-distributed data \cite{Tanabashi:2018oca}:

\begin{equation}
    \chi^2 = -2\log\mathcal{L} = 2\sum_i^{N_{\rm bins}}\left[ M_i-D_i+D_i\ln\left({D_i\over M_i}\right) \right]
\end{equation}

where $M_i$ is the \dword{mc} %Monte Carlo 
expectation in bin $i$ and $D_i$ is the observed count. Most often the bins here represent reconstructed neutrino energy, but other observables, such as reconstructed kinematic variables or event classification likelihoods may also be used. Multiple samples with different selections can be fit simultaneously, as can multi-dimensional distributions of reconstructed variables.

Event records representing the reconstructed properties of neutrino interactions and, in the case of  \dword{mc}, the true neutrino properties are processed to fill the required histograms. Oscillated \dword{fd} predictions are created by populating \twod histograms, with the second axis being the true neutrino energy, for each oscillation channel ($\nu_\alpha\to\nu_\beta$). These are then reweighted as a function of the true energy axis according to an exact calculation of the oscillation weight at the bin center %\todo{did joao ever write up PMNSOpt?} 
and summed to yield the total oscillated prediction:

\begin{equation}
    M_i = \sum_\alpha^{e,\mu}\sum_\beta^{e,\mu,\tau}\sum_j P_{\alpha\beta}(E_j)M_{ij}^{\alpha\beta}
    \label{eqn:cafana_ll}
\end{equation}

where $P_{\alpha\beta}(E)$ is the probability for a neutrino created in flavor state $\alpha$ to be found in flavor state $\beta$ at the \dword{fd}. $M_{ij}^{\alpha\beta}$ represents the number of selected events in bin $i$ of the reconstructed variable with true energy $E_j$, taken from a simulation where neutrinos of flavor $\alpha$ from the beam have been replaced by equivalent neutrinos in flavor $\beta$. Oscillation parameters that are not displayed are profiled over using {\sc minuit}~\cite{James:1994vla}. That is, their values are set to those that produces the best match with the simulated data at each point in parameter space.

The impact of systematic uncertainties is included by adding additional nuisance parameters into the fit. Each of these parameters can have arbitrary effects on the \dword{mc} prediction, and is profiled over in the production of the result. The range of these parameters is controlled by the use of Gaussian penalty terms to reflect our prior knowledge of reasonable variations.

For each systematic parameter under consideration, the matrices $M_{ij}^{\alpha\beta}$ are evaluated for a range of values of the parameter, by default $\pm1,2,3\sigma$. The predicted spectrum at any combination of systematic parameters can then be found by interpolation. Cubic interpolation is used, which guarantees continuous and twice-differentiable results, advantageous for gradient-based fitters such as {\sc minuit}. %\todo{worth including a picture of this?}

For many systematic variations, a weight can simply be applied to each event record as it is filled into the appropriate histograms. For others, the event record itself is modified, and for a few systematic uncertainties it is necessary to use an entirely separate sample that has been simulated with some alteration made to the simulation parameters.

For some systematic uncertainties, such as uncertainties on the neutrino flux (Section \ref{sec:nu-osc-05}), the natural treatment leads to a large number of parameters that have strongly-correlated effects on the predicted spectrum. In this case, Principal Component Analysis is used to create a greatly reduced set of systematic parameters which cover the vast majority of the allowed variation, and also present fewer degeneracies to the fitter.

Information from the \dword{nd}, which is used to constrain systematic uncertainties, is included via additional $\chi^2$ contributions (Equation \ref{eqn:cafana_ll}) without oscillations. Specific \dword{nd} samples such as neutrino-electron elastic scattering and off-axis samples may be included separately. %\todo{is this enough to foreshadow DUNE Prism?}

External constraints, for example from solar experiments, can be included as an arbitrary term in the $\chi^2$ depending on the oscillation parameters. In practice, a quadratic term, corresponding to a Gaussian likelihood, will be used for results in this section.

\subsection{Sensitivity Studies}
\label{sect:methods-dunefits}
\fixme{Expand section as results are produced}
\dword{dune} sensitivity studies are performed using the \dword{cafana} framework described in the previous section. Fits for sensitivity to \dword{cpv}, neutrino mass ordering, and octant are performed, in addition to 1D and \twod %one- and two-dimensional 
fits for oscillation parameter resolution.
The experimental sensitivity is quantified using a test statistic, $\Delta\chi^2$, which is calculated by comparing the predicted spectra for alternate hypotheses. These quantities are defined, differently for neutrino mass ordering, $\theta_{23}$ octant, and \dword{cpv} sensitivity to be:
\begin{eqnarray}
\Delta\chi^2_{\textrm{ordering}} & = & \chi^2_{\textrm{opposite}} - \chi^2_{\textrm{true}} \label{eq:dx2_MH}\\
\Delta\chi^2_{\textrm{octant}} & = & \chi^2_{\textrm{opposite}} - \chi^2_{\textrm{true}} \\
\Delta\chi^2_{\textrm{CPV}} & = & \textrm{Min}[\Delta\chi^2_{CP}(\mdeltacp^{\textrm{test}}=0),\Delta\chi^2_{CP}(\mdeltacp^{\textrm{test}}=\pi)],
\end{eqnarray}
where $\Delta\chi^2_{CP} = \chi^{2}_{\mdeltacp^{test}} - \chi^2_{\mdeltacp^{true}}$, and $\chi^2$ is defined in Equation~\ref{eqn:cafana_ll}. Since the true value of \deltacp is unknown, a scan is performed over all possible values of $\mdeltacp^{true}$. Both the neutrino mass ordering and the $\theta_{23}$ octant are also assumed to be unknown and are varied in the fits, with the lowest value of $\Delta\chi^2$ thus obtained used to estimate the sensitivities. 

Similarly, expected resolution for oscillation parameters is determined by scanning the value of the oscillation parameter of interest and comparing spectra produced by the varied test value with that of the ``true'' central value. The one-sigma resolution is defined as the difference between the true and test value at which the test statistic, $\Delta\chi^2$, is greater than one, taking the average resolution to allow for cases in which the difference is not symmetric about the true value. In these fits, the oscillation parameter of interest is fixed while the others are free in the fit, with constraints from external measurements applied. Similarly, for the \twod parameter sensitivity plots, the two oscillation parameters of interest are fixed in the fit and scanned over. The \twod allowed region is chosen to be the area inside which the fit test statistic is less than the appropriate $\chi^2$ critical value for two degrees of freedom (e.g., the 90\% \dword{cl} curve is for a critical value of the test statistic of 4.61).

Details of these fits are still being finalized -- this section will be updated to describe fit input samples and systematic uncertainties. Data samples included in the \dword{dune} fits presented here are expected to include \dword{fd} \numutonumu and \numutonue samples as well as $\nu_\mu$ \dword{cc} samples, both on- and off-axis, from the \dword{lartpc} \dword{nd}, neutrino-electron elastic scattering samples from the \dword{lartpc} \dword{nd}, and samples from the \dword{gartpc} \dword{nd}. Systematic uncertainties include oscillation parameter variations, flux uncertainties using the \dword{pca} analysis described in Section~\ref{sect:methods-cafana}, neutrino interaction model uncertainties based primarily but not exclusively on \dword{genie} driven uncertainties, and assorted detector uncertainties. These sources of systematic uncertainty and the way they are implemented in the analysis are described in more detail in the following sections.
