% Collected here for convenience - NOT used in the TeX build. -- NOT complete  4/17/18

% PD Bibiography - not included yet - rjw 2/21/18
%For the TDR, we have created the file common/tdr-citedb.bib to contain all the citations. Please
% read the guidelines at the beginning of that file. We have left a well-populated common/citedb.bib
% in the TDR directory in case you want to search for a citation that may have appeared in the
% CDR, or other DUNE/LBNF document



\begin{thebibliography}{1}
%Denver
\bibitem{bib:JINST-11-C05019}
D.~Whittington.
\newblock Photon detection system designs for the deep underground neutrino
  experiment.
\newblock {\em Journal of Instrumentation}, 11(05):C05019, 2016.

\bibitem{bib:mu2e_tdr}
L. Bartoszek \textit{et al.}.
\newblock Mu2e Technical Design Report.
\newblock arXiv:1501.05241.

\bibitem{bib:DoubleShiftLG-NIM-171113}
B.~Howard, S.~Mufson, D.~Whittington, B.~Adams, B.~Baugh, J.~Jordan, J.~Karty,
  C.~Macias, and A.~Pla-Dalmau.
\newblock {A Novel Use of Light Guides and Wavelength Shifting Plates for the
  Detection of Scintillation Photons in Large Liquid Argon Detectors}.
\newblock {\em Nucl. Instrum. Meth.} (submitted).
\newblock FERMILAB-PUB-17-488-ND-PPD.
\newblock arXiv:1710.11233.

\end{thebibliography}

\end{document}



\begin{thebibliography}{99}
% Ana
\footnotesize{

\bibitem{arapuca_jinst} A.A. Machado and E. Segreto, Journal of Instrumentation, 11, C02004 (2016).

\bibitem{VIKUITI}
	3M VIKUITY foils. https://en.wikipedia.org/wiki/Vikuiti.
    
\bibitem{arpkLNLS} H. daMotta, A.A. Machado, L. Paulucci, E. Segreto, B. Gelli, M.R. Guzzo, G. Marques, D. Galante, V. Teixeira, W. Araujo, C. Ambrosio, M.Bissiano, F. Marinho. {\bf"ARAPUCA light trap for large liquid argon time projection chambers"}
    https://pos.sissa.it/295/153/pdf

}
\end{thebibliography}

\end{document}


@article{Grace:2015yta,
      author         = "Grace, Emily and Nikkel, James A.",
      title          = "{Index of refraction, Rayleigh scattering length, and
                        Sellmeier coefficients in solid and liquid argon and
                        xenon}",
      journal        = "Nucl. Instrum. Meth.",
      volume         = "A867",
      year           = "2017",
      pages          = "204-208",
      doi            = "10.1016/j.nima.2017.06.031",
      eprint         = "1502.04213",
      archivePrefix  = "arXiv",
      primaryClass   = "physics.ins-det",
      SLACcitation   = "%%CITATION = ARXIV:1502.04213;%%"
}
