\chapter{Calibration Hardware for Single-Phase}
\label{ch:sp-calib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Introduction}
\label{sec:sp-calib-ov}

\input{vol-sp/ch-sp-calib/overview}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cleardoublepage

\section{Calibration Systems}

\dword{dune} plans to build two primary systems dedicated to the calibration of the single-phase far detector TPC: a laser system
and a \dlong{pns} system. The laser system is aimed at the determination of the \efield, mapping an essential parameter for the description of the detector performance. Two laser systems are planned. With a high intensity laser, charge can be created in long straight tracks in the detector by direct ionization of \dword{lar} with the laser beams. This is described in Section~\ref{sec:sp-calib-sys-las-ion}. On the other hand, laser excitation of targets placed in the cathode creates additional charge from well-defined locations that can be used to monitor the TPC. This is described in Section~\ref{sec:sp-calib-sys-las-pe}. The \dword{pns} system is aimed at the performance validation in the low energy regime. This is described in detail in Section~\ref{sec:sp-calib-sys-pns}.

The physics motivation, requirements and design of these systems are described in the following subsections. Alternative designs
%Non-baseline alternatives 
for the ionization laser system, as well as the proposed radioactive source deployment system, are described in the Appendix, in Sections~\ref{sec:sp-calib-laser-alter} and \ref{sec:sp-calib-sys-rsds}, respectively.

%\subsection{Ionization Laser System}
%\label{sec:sp-calib-sys-las}

%Two laser systems are planned. With a high intensity laser, charge can be created in long straight tracks in the detector by direct ionization of \dword{lar} with the laser beams. This is described in Section~\ref{sec:sp-calib-sys-las-ion}. On the other hand, laser excitation of targets placed in the cathode creates additional charge from well-defined locations that can be used to monitor the TPC. This is described in Section~\ref{sec:sp-calib-sys-las-pe}.
%The next sections describe the two subsystems based on these effects.

\input{vol-sp/ch-sp-calib/laser-ionization}

\input{vol-sp/ch-sp-calib/laser-positioning}

%\subsection{Photoelectron Laser System}
\input{vol-sp/ch-sp-calib/laser-photoelectron}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pulsed Neutron Source System}
%Source Calibration System}
\label{sec:sp-calib-sys-pns}
 
\input{vol-sp/ch-sp-calib/neutron-source}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\subsection{Proposed System: Radioactive Source Calibration System}
%\label{sec:sp-calib-sys-rs}

% \fixme{Call it "deployment" or "calibration" system?}
%\input{vol-sp/ch-sp-calib/radioactive-sources}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Additional Systems Considered: External Muon Tracker}
%\label{sec:sp-calib-addl}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{External Muon Tagger}
%\fixme{you can't have just one subsection; if it's only the muon tagger, then let's put this in the section heading}
%\input{vol-sp/ch-sp-emt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Cryostat Configuration for Calibration}
%\label{sec:sp-calib-cryocfg}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
%changed from subsection to section
\subsection{Validation of Calibration Systems}
\label{sec:sp-calib-val}
\input{vol-sp/ch-sp-calib/validation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{DAQ Requirements}
\label{sec:sp-calib-daqreq}
\input{vol-sp/ch-sp-calib/daq-calib}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
\section{Organization and Management}
\label{sec:sp-calib-org}
\input{vol-sp/ch-sp-calib/org}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Institutional Responsibilities}
\label{sec:sp-calib-resp}
\input{vol-sp/ch-sp-calib/institute-resp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cost and Labor}
\label{sec:sp-calib-cost}
\input{vol-sp/ch-sp-calib/cost}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Schedule and Milestones}
\label{sec:sp-calib-sched}
\input{vol-sp/ch-sp-calib/schedule}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Risks}
\label{sec:sp-calib-risks}
\input{vol-sp/ch-sp-calib/risks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interfaces}
\label{sec:sp-calib-intfc}
\input{vol-sp/ch-sp-calib/intfc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Installation, Integration and Commissioning}
\label{sec:sp-calib-iic}
\input{vol-sp/ch-sp-calib/iic}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quality Control}
\label{sec:sp-calib-qc}
\input{vol-sp/ch-sp-calib/qc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Safety}
\label{sec:sp-calib-safe}
\input{vol-sp/ch-sp-calib/safety}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
%%%%%%%%%%%%%%%%%% Appendix starts here %%%%%%%%%%
%\appendix
%begin{appendices}
\fixme{SG: tried to create an appendix but it is coming out weird. Contacted Anne about this. For now make this a section called "Appendix"}

\section{Appendix}
\subsection{Laser System Alternative Designs}
\label{sec:sp-calib-laser-alter}
\input{vol-sp/ch-sp-calib/laser-alternatives}

\subsection{Proposed Radioactive Source Calibration System}
\label{sec:sp-calib-sys-rsds}
\input{vol-sp/ch-sp-calib/radioactive-sources}

%\end{appendices}
