\chapter{Installation}
\label{ch:sp-tc}

This chapter covers all the work and infrastructure required to install an SP detector module. 
Before getting into the details, we first provide some reminders of the scale of the task, beginning with the two facts that drive all others: A DUNE FD module is enormous, with outer cryostat dimensions length$\times $width$\times $height$=$ $62\times 19\times 18$ m$^{3}$; and every piece of the FD module must travel $1500$ \si{m} down the Ross shaft to the 4850 level of SURF and be transported to the detector caverns.

For the \dword{tpc}, 150 \dword{apa}s, each $6.0$ m high and $2.3$ m wide and  weighing $600$ kg with $3500$ strung sense and shielding wires, must be taken down the shaft as special \textquotedblleft slung loads\textquotedblright and moved to the area outside the \dword{dune} cryostat. 
The \dword{apa} are moved into a pre-prepared length$\times $width$\times $height$=$ $30\times 19 \times 17\ {\rm or}\ 10$ m$^{3}$ clean room where they are first be outfitted  with photon detector units and passed through a series of qualification tests.
Here two APAs are linked into a vertical 12 m high double unit, connect to readout electronics, receive a cold-test in place, and then move into the cryostat to be connected at the proper location on the previously installed detector support structure (DSS) and cabled up with the feedthroughs. 
In parallel the field cages that define the \dword{tpc} active volume must be installed with all their high voltage connections, along with  elements of the cryogenic instrumentation and slow control (CISC) and calibration systems.

After twelve months of detector component installation, which follows twelve months of detector infrastructure installation, the cryostat closes (with the last installation steps occurring in confined space accessed through a narrow human access port). 
Following leak checks, final electrical connection tests, and installation of the neutron calibration source, the process of filling the cryostat with $17,000,000$ kg of LAr begins.

From this terse summary, it is clear that installation requires meticulous planning and execution of thousands of tasks by well-trained teams of technicians, riggers, and detector specialists. 
High level requirements for these tasks are spelled out in Table \ref{tab:specs:just:SP-TC} and the text that follows. 
In all the planning and future work the requirement that subsumes all others in the installation process is safety safety. DUNE's goal is zero accidents resulting in personal injury, damage to detector components, or harm to the environment.

\input{generated/req-just-SP-TC.tex}

Installation of the DUNE FD presents a multitude of hazards that includes  manipulation heavy loads in the tight spaces of the mine and detector module,  working at considerable heights above the floor, repeated utilization of large volumes of cryogens, multiple tests with high voltage, commissioning of a class IV laser system, and deployment of a high activity neutron source. Mitigation of these hazards begins with the strong professional on-site ES\&H\ teams of the Fermilab South Dakota Services Division (SDSD) and the host SURF lab.
All installation team members, both at the surface and underground, will undergo rigorous formal safety training that will be update at daily intervals. Any team member can stop work at any time for safety purposes. Further details of the overall DUNE safety plan are provided in Chapter 9 of the Technical Coordination Volume of the TDR. In addition, each section of this chapter provides further details on the evolving safety plan for installation. This plan has been informed by the successful safety experience of SURF with other underground experiments (e.g., LUX, Majorana Demonstrator, LZ), DUNE members in executing projects at other underground locations (e.g., MINOS at Soudan, Minnesota, USA), at other locations remote from major international laboratories (e.g., Daya Bay, China and No$\nu $a Far Detector (Ash River, Minnesota, USA), and at the home laboratories of both Fermilab and CERN.

\input{generated/risks-longtable-SP-FD-JPO}


As part of the \dword{dune} design process the detector components and the TPC have been prototyped at various stages. The \dword{protodune}-SP prototype which was assembled from full scale dune components has recently been completed and has taken data. 
This process has been extremely important in planning the far detector installation. A detailed list of lessons learned from \dword{protodune}-SP construction and installation was compiled.\cite{bib:docdb8255} 
These lessons learned and other experience from the team planning the installation was used to develop a list of \textquotedblleft risks \textquotedblright for the \dword{dune} installation. 
The risk register documents what could be improved from the \dword{protodune} installation and what people felt could go wrong in the \dword{dune} installation. After the list of risks are generated plans to prevent the risks from occurring or minimizing the impacting to the project are formulated as mitigation strategies. These plans to improve what was done in \dword{protodune} or prevent difficulties at \dword{dune} are then built into the \dword{dune} installation plan. The list of risks associated with the \dword{dune} installation are shown in Table \ref{tab:INSTALL-risks}. The risks in Table \ref{tab:INSTALL-risks} are considered the highest impact risks where a dedicated mitigation strategy is required. All the lessons learned from \dword{protodune} will be factored into the detailed installation planning.

This  installation chapter is divided into three main sections describing the main divisions of work. First the logistics section describes how material will be delivered to the South Dakota region and then forwarded to the Ross headframe on the \dword{surf} site for transport underground. A warehouse facility is used for buffering materials prior to transport to \dword{surf}, inventorying shipments, consolidating packages, and coordinating with the  \dword{cf}-\dword{cmgc}. The second section describes all the infrastructure needed to install and operated the detector. This includes the cleanroom for installation and its contents but also infrastructure like racks, cable trays, storage facilities and machining facilities. The third section describes the actual installation process itself which is divided into 3 phases: the \dword{cuc} setup phase, the installation setup phase, and the detector installation phase. 


\input{vol-sp/ch-sp-tc/logistics}


\input{vol-sp/ch-sp-tc/infrastructure}

\input{vol-sp/ch-sp-tc/itf}

\input{vol-sp/ch-sp-tc/installation}

\input{vol-sp/ch-sp-tc/cost-sched-risk}

\input{vol-sp/ch-sp-tc/esh-test.tex}
