%\chapter{Near detector executive summary}
%\label{ch:exsum-nd}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Role of the near detector in DUNE}
\label{sec:exsum-nd-role}
%\input{vol-physics/nd-phys-from-LBNE-doc}

%very brief overview of various parts of the mission and the need for the nd

The near detector (ND) is an important tool for constraining the systematic uncertainties of the oscillation measurements. The aim of the DUNE experiment is to measure the oscillation probabilities for muon neutrino and muon antineutrinos to either stay the same flavor or oscillate to electron (anti)neutrinos. Measuring these probabilities as a function of the neutrino energy will allow the extraction of the mass ordering (MO) and the CP-violating phase \deltacp. In this portion of the executive summary we concentrate on the near detector's role in the oscillation measurement.

The DUNE ND will also have a physics program of its own measuring cross sections, non-standard interactions, searching for sterile neutrinos, dark photons and other exotic particles. These are (important) secondary aims that expand the physics impact of the ND complex.  Also the cross section program is coupled to the oscillation measurement in so far as the cross-sections and smearing functions used in the oscillation analysis will likely come from a MC tuned with standalone cross-section measurements.

The DUNE far detector (FD) will not measure the neutrino oscillation probability directly. Instead, it will measure the neutrino interaction rate for different neutrino flavors as a function of the reconstructed neutrino energy. It is educational to formalize the measurements that are performed in the near and far detectors in the following equations:
\begin{align}
\label{eq:fdrate}
\frac{dN^{FD}_{x}}{dE_{rec}}(E_{rec}) & = 
\int \Phi^{FD}_{\numu}(E_\nu)P_{\numu\rightarrow x}(E_\nu)\sigma^{Ar}_x(E_\nu)T^{FD,Ar}_x(E_\nu,E_{rec})dE_\nu\\
\frac{dN^{ND}_{x}}{dE_{rec}}(E_{rec}) & = 
\int \Phi^{ND}_{x}(E_\nu)\sigma^m_x(E_\nu)T^{d,m}_x(E_\nu,E_{rec})dE_\nu\\
\mbox{with\hspace{2cm} } x & = \nue , \numu \nonumber \\
d & = \mbox{detector index} \nonumber \\
m & = \mbox{interaction target/material, (eg. H, C, or Ar)} \nonumber \\
E_\nu & = \mbox{true neutrino energy} \nonumber \\
E_{rec} & = \mbox{reconstructed neutrino energy} \nonumber \\
T^{d,m}_x(E_\nu,E_{rec}) & = \mbox{true to reconstruction transfer function} \nonumber \\
\sigma^m_x(E_\nu) & = \mbox{neutrino interaction cross section} \nonumber \\
\Phi^{d}_x(E_\mu) & = \mbox{un-oscillated neutrino flux} \nonumber \\
\frac{dN^{d}_{x}}{dE_{rec}}(E_{rec}) & = \mbox{measured differential event rate per target (nucleus/electron)} \nonumber 
\end{align}
There are equivalent formulae for anti-neutrinos. For simplicity, the instrumental backgrounds (wrongly selected events) and the intrinsic beam contaminations (\nue interactions in case of the appearance measurement) have been ignored. But an important function of the near detector is also to quantify and characterize those backgrounds.

It is not possible to constrain the FD neutrino flux directly, but the near-to-far flux ratio is believed to be tightly constrained by existing hadron production data and the beamline optics. As such eq.\,\ref{eq:fdrate} can be rewritten as 
\begin{align*}
\frac{dN^{FD}_{x}}{dE_{rec}}(E_{rec}) & = 
\int \Phi^{ND}_{\numu}(E_\nu)R(E_\nu)P_{\numu\rightarrow x}(E_\nu)\sigma^{Ar}_x(E_\nu)T^{d,Ar}_x(E_\nu,E_{rec})dE_\nu\\
& \mbox{with } R(E_\nu) = \frac{\Phi^{FD}_{\numu}(E_\nu)}{\Phi^{ND}_{\numu}(E_\nu)} \mbox{ taken from the beam simulation} \nonumber
\end{align*}

It is not possible to measure only a near-to-far event ratio and extract the oscillation probability since many effects do not cancel trivially.  This is due to the non-diagonal true-to-reconstruction matrix, which not only depends on the underlying differential cross section, but also on the detector used to measure a specific reaction.
\begin{align*}
\frac{dN^{FD}_{x}}{dE_{rec}}(E_{rec})/{\frac{dN^{ND}_{\numu}}{dE_{rec}}(E_{rec})} & \neq  R(E_\nu)P_{\numu\rightarrow x}(E_\nu)\frac{\sigma^{Ar}_x(E_\nu)}{\sigma^{m}_{\numu}(E_\nu)}
\end{align*}
It is therefore important that the DUNE ND suite constrains as many components as possible.

\subsection{Constraining the Flux}
\label{sec:flux}
While the near-to-far flux ratio is tightly constrained to the level of 1-2\%, the same is not true for the absolute flux itself. T2K, using hadron production data obtained from a replica target, can constrain the absolute flux at the near detector to 5-6\% in the peak region and to around 10\% in most of its energy range. The NuMI beam has been constrained to 8\% using a suite of thin target hadron production data. The better the near-detector flux is known, the easier it is to constrain modeling uncertainties by measuring flux-integrated cross sections. Predicting the event rate at the far detector to a few \% will require additional constraints to be placed with the near detectors or substantial improvements in our understanding of the hadron production and focusing uncertainties. 

There are several handles to constrain the flux, which are addressed below. Briefly they offer the following constraints:

\begin{itemize}
    \item The overall flux normalization can be constrained by measuring neutrinos scattering off of atomic electrons.
    \item The energy dependence ("shape") of the \numu and \anumu %\numubar
     flux can be constrained using the "Low-$\nu$" scattering process.
    \item The flux ratio $\anumu/\numu$ can be constrained using charged current coherent neutrino scattering.
    \item The $\nue/\numu$ flux ratio in the energy region that standard oscillation occurs in is well constrained by the beam simulation. The experiment can also measure the $\nue/\numu$ interaction ratio and constrain the flux ratio using cross section universality.
\end{itemize}


% event rates table
% GArTPC numbers from HPTPC report doc-6652
% numubar CC coherent is 12% of numu CC coherent according to doc-273
% (this is numubar in numu beam mode)
\begin{dunetable}[Event rates for flux constraining processes]{lll}{fluxrates}{Event rates for processes that can be used to constrain the neutrino flux. The rates are given per year for a \SI{1}{ton} GArTPC and a \SI{25}{ton} LArTPC \cite{bib:docdb6652}. The flux is from the simulated "2017 engineered" LBNF beam with a primary momentum of \SI{120}{GeV/c} and \SI{1.1e21}{POT/year}. The detectors are assumed to be on-axis.}
Event class & GArTPC & LArTPC \\ \toprowrule
\numu + $e^-$ elastic ($E_e>\SI{500}{MeV}$) & \num{1.3e2} & \num{3.3e3} \\ \colhline
\numu low-$\nu$ ($\nu<\SI{250}{MeV})$ & \num{2.1e5} & \num{5.3e6} \\ \colhline
\numu CC coherent & \num{8.8e3} & \num{2.2e5} \\ \colhline
\anumu CC coherent & \num{8.4e2} & \num{2.1e4} \\ \colhline
\end{dunetable}
 
%Raw numbers without acceptance, for 1 year, assuming 25t FV, but 1.1E21 POT of the new 120GeV "2017 engineered" flux:

%nu+e (Ee > 500 MeV) 3300
%FHC numu CC coherent 2.2 E5
%FHC numubar CC coherent 2.1 E4

%numu CC reco nu < 250 MeV 7.8 E6
%numu CC true nu < 250 MeV 5.3 E6
%Where reco is summing all hadronic energy deposits but without making corrections for recomb, etc. so it only feeds down, hence the larger number of reco.

%The 2500 number for nu+e includes what we think is a conservative acceptance on top of the threshold cut, and is for the old 80GeV flux. % The 135 number for gas TPC definitely assumes 100% acceptance above threshold, so the analogous number is 3300.

%If you want numbers after acceptance (i.e. selected events) I can also provide estimates of those.


\subsubsection{Neutrino-Electron Elastic Scattering}

%The reactions $\nux \ e^-\rightarrow \nux \ e^-$ and $\anux \ e^-\rightarrow\anux \ e^-$ are pure electroweak processes, which have been calculated to high precision. The cross section is different for neutrinos and anti-neutrinos. It is identical for $\numu$ and $\nutau$. There is an additional charged-current process for $\nue$, which enhances the total cross section by about a factor of 6 for $\nue$ relative to $\numu$ and $\nutau$. It is, however, approximately 2000$\times$ smaller than the elastic scattering on a nucleon and this process therefore suffers from low statistics. It can be used to constrain the flux integral and it has been shown that one can also constrain the differential flux by analyzing the electron kinematics.  The target material for this measurement is not very important since the scattering is on atomic electrons. However, the ability to identify electrons and separate them from background reactions such as quasi-elastic neutrino-electron scattering is essential.

%Measurements of neutrino-nucleus scattering are sensitive to the product of the flux and cross section, both of which are uncertain. This can lead to a degeneracy between flux and cross section nuisance parameters in the oscillation fit, and result in significant anti-correlations, even when the uncertainty on the diagonal component is small. One way to break this degeneracy is by including a sample for which the a priori cross section uncertainties are very small. 

Neutrino-electron scattering ($\nu \ e \rightarrow \nu \ e$) is a pure electroweak process with calculable cross section at tree level. The final state consists of a single electron, subject to the kinematic limit 

\begin{equation}
1 - \cos \theta = \frac{m_{e}(1-y)}{E_{e}},
\end{equation}

where $\theta$ is the angle between the electron and incoming neutrino, $E_{e}$ and $m_{e}$ are the electron mass and total energy, respectively, and $y = T_{e}/E_{\nu}$ is the fraction of the neutrino energy transferred to the electron. For DUNE energies, $E_{e} \gg m_{e}$, and the angle $\theta$ is very small, such that $E_{e}\theta^{2} < 2m_{e}$. 

The overall flux normalization can be determined by counting $\nu \ e \rightarrow \nu \ e$ events. Events can be identified by searching for a single electromagnetic shower with no other visible particles. Backgrounds from $\nu_{e}$ charged-current scattering can be rejected by looking for large energy deposits near the interaction vertex, which are evidence of nuclear breakup. Photon-induced showers from neutral-current $\pi^{0}$ events can be distinguished from electrons by the energy profile at the start of the track. The dominant background is expected to be $\nu_{e}$ charged-current scattering at very low $Q^{2}$, where final-state hadrons are below threshold, and $E_{e}\theta^{2}$ happens to be small. The background rate can be constrained with a control sample at higher $E_{e}\theta^{2}$, but the shape extrapolation to $E_{e}\theta^{2} \rightarrow 0$ is uncertain at the 10-20\% level.

For the DUNE flux, approximately 100 events per year per ton of fiducial mass ar expected with electron energy above 0.5 GeV. For a LAr TPC mass of 25 tons, this corresponds to 3300 events per year. The statistical uncertainty on the flux normalization from this technique is expected to be $\sim$1\%. \minerva has achieved a systematic uncertainty just under 2\% and it seems plausible that \dune could do at least as well\cite{bib:minervanue}. 


\subsubsection{The Low-$\nu$ method}
The inclusive cross section for CC scattering $(\nu_l+N\rightarrow l^-+X)$ does not depend on the neutrino energy in the limit where the energy transfered to the nucleus $\nu = E_\nu-E_{l} $ is zero~\cite{bib:original_lownu}.  In that limit, the event rate is proportional to the flux, and by measuring the rate as a function of energy, one can get the flux "shape". This measurement has been used in previous experiments and has the potential to provide a constraint in \dune with a statistical uncertainty $<1\%$.

In practice, one cannot measure the rate at $\nu=0$. Instead it is necessary to restrict $\nu$ to be less than a few \SI{100}{MeV}.  This introduces a relatively small $E_\nu$ dependence into the cross-section that must be accounted for to obtain the flux shape. Thus the  measurement technique depends on the cross-section model but the uncertainty is manageable~\cite{bib:bodek_lownu}. This is particularly if low energy protons and neutrons produced in the neutrino interaction can be detected. 

\subsubsection{Coherent Neutrino-nucleus Scattering}
The interactions $\nu_l + A \rightarrow l^- + \pi^+ + A$ and 
%$\nubar_l + N   & \rightarrow l^+ + \pi^- + N$ 
\fixme{change nubar to anu- per defs.tex file - and fix expression. Anne}
occur with very low three momentum transfer to the target nucleus (A). As such, the interactions proceed coherently with the entire nucleus, and do not suffer from nuclear effects (though background channels certainly do). These coherent interactions are most useful as a constraint on the $\anumu/\numu$ flux ratio. Identifying with high efficiency and purity requires a detector with excellent momentum and angular resolution.

\subsubsection{Beam \nue content}

{\it Text to be added.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview of the near detector}
\label{sec:exsum-nd-overview}
%\input{vol-physics/nd-phys-from-LBNE-doc}

high level schematic of parts and complementarity in the mission

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Liquid argon TPC}
\label{sec:exsum-nd-lartpc}
%\input{vol-physics/nd-phys-from-LBNE-doc}

% This was written for the LBL chapter but is going to be cut for length, does it fit here?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Multi-purpose detector}
\label{sec:exsum-nd-mpt}
%\input{vol-physics/nd-phys-from-LBNE-doc}

\subsection{High pressure gas TPC}
\label{ssec:exsum-nd-mpt-gtpc}
brief summary of the gTPC design/performance

\subsection{Electron calorimeter}
\label{ssec:exsum-nd-mpt-ecal}
brief summary of the ECAL design/performance

\subsection{Magnet}
\label{ssec:exsum-nd-mpt-magnet}
brief summary of the magnet design

\subsection{Muon system}
\label{ssec:exsum-nd-mpt-muon}
brief summary of the muon system design

\subsection{Three dimensional scintillator tracker}
\label{ssec:exsum-nd-mpt-3DST}
brief summary of design and performance of 3DST, this may be promoted to a section rather than subsection if it is located outside of the MPT

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{DUNE-PRISM}
\label{sec:exsum-nd-DP}
%\input{vol-physics/nd-phys-from-LBNE-doc}

summary of DP concept in somewhat more depth than in ND overview section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{ND hall}
\label{sec:exsum-nd-hall}
%\input{vol-physics/nd-phys-from-LBNE-doc}

Overview of the ND hall facility

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Long baseline oscillation physics}
\label{sec:exsum-nd-role-lbl}

Summary of requirements and performance of ND complex in LBL work

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Beam monitoring}
\label{sec:exsum-nd-role-bm}

summary of requirements and performance of ND complex in beam monitoring

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Near detector physics}
\label{sec:exsum-nd-role-ndphysics}

This will be BSM, including short baseline oscillations, and conventional nd-only physics, plus summary of requirements and performance

\subsection{Beyond the Standard Model physics}
\label{ssec:exsum-nd-ndphys-bsm}

\subsection{Standard Model physics}
\label{sec:exsum-nd-ndphys-sm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary of near detector requirements and goals}
\label{sec:exsum-nd-requirements}
