
%\fixme{SG, KM: Done; JM please check. }
%To-DO: Need more information on requirements from neutron source and RA source, once we have it, we can update the text/table as needed.}

Some common design considerations for calibration devices include stability, reliability, and longevity, so calibration systems can be operated for the lifetime of the experiment (\dunelifetime). Such longevity is uncommon for any device, so the overall design permits replacing devices where possible, namely the parts that are external to the cryostat. The systems must also adhere to relevant global requirements of the \dword{dune} detector. Table~\ref{tab:specs:SP-CALIB} shows the top-level overall requirements for calibration subsystems along with global \dword{dune} requirements that are relevant for calibration. For example, \dword{dune} requires the \efield  on any instrumentation devices inside the cryostat to be less than 30 kV/cm to minimize the risk of dielectric breakdown in \dword{lar}. Another consideration important for reconstructing events is the maximum noise level the readout electronics can tolerate from calibration devices. \dword{pdsp} is evaluating this. In Table~\ref{tab:specs:SP-CALIB}, two values are quoted for most of the parameters: i) {\it specification}, which is the minimum requirement to guarantee baseline performance, and ii) {\it goal}, an ideal requirement enabling more detailed studies and for achieving improved precision.

For the ionization laser system, the energy and position reconstruction requirements for physics measurements lead to requirements for the necessary precision in measuring the \dword{tpc} \efield as well as its spatial coverage and granularity. The precision of the \efield measurement with the laser system must be about \SI{1}{\%} so that the effect from \efield on the collected charge, via the dependence of the recombination factor on \efield, is well below \SI{1}{\%}. This is also motivated by consistency with the high level \dword{dune} specification of \SI{1}{\%} on field uniformity throughout the volume for component alignment and the \dword{hv} system. For laser coverage, to keep the \efield measurement at the $\sim$\SI{1}{\%} level, we are aiming for a coverage of \SI{75}{\%} or more of the total \dword{fv}. The requirement on granularity for the laser is estimated based on the \dword{fv} uncertainty requirements (\SI{1}{\%}) and corresponding uncertainty requirements (\SI{1.5}{\cm}) in each coordinate. A specification is set for a voxel size of \num{30}$\times$\num{30}$\times$\SI{30}{\cubic\cm}, that should be sufficient to satisfy the \dword{fv} uncertainty requirements. A goal is set for \num{10}$\times$\num{10}$\times$\SI{10}{\cubic\cm}, which could allow for a refinement in precision in some detector regions. 

The laser beam location must also meet the level of reconstruction requirement in each coordinate, approximately \SI{5}{\milli\m}. In order to reach that over distances of up \SI{20}{\m}, where the latter is the maximum distance that any beam needs to travel to cover all detector voxels, this results in a stringent requirement of \ang{0.015} (or \SI{0.25}{\mrad}) on the pointing precision. The laser beam location system is also designed to check the beam location with a precision of \SI{5}{\milli\m} over distances of up \SI{20}{\m}.
%\SI{5}{\milli\m} over \num{5} to \SI{10}{\m}, where the latter is the distance between two consecutive laser ports in the beam direction. This results in a stringent requirement of \ang{0.03} (or \SI{0.5}{\mrad}).
The data volume for the ionization laser system must be at least \num{184}~TB/year/\SI{10}{\kt}, assuming \num{800}k laser pulses, \num{10}$\times$\num{10}$\times$\SI{10}{\cubic\cm} voxel sizes, a \SI{100}{\micro\s} zero suppression window, and two dedicated calibration campaigns per year.

For the \dword{pns} system, the system must provide sufficient neutron event rate to make spatially separated precision measurements across the detector of a comparable size to the voxels probed by the laser (\num{30}$\times$\num{30}$\times$\SI{30}{\cubic\cm}) for most regions of the detector (\SI{75}{\%}). 
%The laser and \dword{pns} systems are probing different detector and response parameters, so using one system to propagate the other's calibration to the rest of the detector is not possible.
% 1st draft
%For the supernova program, measurements from the \dword{pns} \fixme{This abbreviation is in neither glossary.} should demonstrate 1\% energy scale, 5\% energy resolution, and 0.5 MeV detection threshold, so each voxel should have sufficient neutron event rate to achieve this. %\todo{KM: Improve or remind connection to SN program? even though it's comparable? SG: maybe for 2nd draft?}
%rewritten for 2nd draft
For the \dword{snb} program, the sensitivity to distortions of the neutrino energy spectrum depends on the uncertainties in the detection threshold and the reconstructed energy scale and resolution. Studies discussed in the physics \dword{tdr} present target ranges for the uncertainties in these parameters~\cite{bib:docdb14068} as a function of energy. The measurements with the \dword{pns} system aim to provide response corrections and performance estimates, so those uncertainty targets are met throughout the whole volume. This ensures that each voxel has sufficient neutron event rate (percent level statistical uncertainty).

%\fixme{Insert correct reference to physics TDR ch7}
%\fixme{Put PNS in glossary and use that.}


In terms of data volume requirements, the \dword{pns} system requires at least \num{144}~TB/year/\SI{10}{\kt} assuming \num{e5} neutrons/pulse, \num{100} neutron captures/\si{\cubic\m},
%m$^{3}$ 
and \num{130} observed neutron captures per pulse, and two calibration runs per year. 

Table~\ref{tab:fdgen-calib-all-reqs} shows the full set of requirements related to all calibration subsystems. More details on each of the requirements can be found under corresponding consortia.   

%\input{generated/req-just-SP-CALIB.tex}

\input{generated/req-longtable-SP-CALIB.tex}

\begin{comment}
%comment the old "hand-made" latex table

\begin{dunetable}
[Top-level specifications for calibration subsystems]
{p{0.45\linewidth}p{0.25\linewidth}p{0.25\linewidth}}
{tab:fdgen-calib-toplevel-reqs} 
{List of Top-Level Specifications for the Calibration Subsystems. Global DUNE requirements are listed in bold.}   Quantity/Parameter	& Specification	& Goal		 \\ \toprowrule      
{\bf Noise from calibration devices}	 & $\ll$ 1000 enc   & \\ \colhline    
{\bf Max. \efield near calibration devices} & < 30 kV/cm & <15 kV/cm \\ \colhline     
Ionization Laser \efield measurement precision & 1\% & <1\% \\ \colhline
Ionization Laser \efield measurement coverage & > 75\% & 100\% \\ \colhline
Ionization Laser \efield measurement granularity & < \num{30}x\num{30}x\num{30}~cm & \num{10}x\num{10}x\num{10}~cm \\ \colhline
Laser beam location precision & 0.5 mrad & 0.5 mrad \\ \colhline
Neutron source coverage & > 75\% & 100\% \\ \colhline % neutron source
Ionization laser data volume (per 10 kton) & 90~TB/year & 185~TB/year\\ \colhline
Neutron source data volume (per 10~kton) & 84~TB/year & 168~TB/year\\ \colhline
Rate of 9~MeV capture $\gamma$-events inside the proposed radioactive source & < 1~kHz & \\ 
\end{dunetable}
\end{comment}

\begin{dunetable}
[Full specifications for calibration subsystems]
{p{0.45\linewidth}p{0.25\linewidth}p{0.25\linewidth}}
{tab:fdgen-calib-all-reqs}
{Full list of Specifications for the Calibration Subsystems.}   
Quantity/Parameter	& Specification	& Goal		 \\ \toprowrule      

Noise from calibration devices	 & $\ll$ 1000 enc   & \\ \colhline    Max. \efield near calibration devices & < 30 kV/cm & <15 kV/cm \\ \colhline                     

\textbf{Direct Ionization Laser System} &    &   \\ \colhline   
\efield measurement precision & 1\% & <1\% \\ \colhline
\efield measurement coverage & > 75\% & 100\% \\ \colhline
\efield measurement granularity & < \num{30}x\num{30}x\num{30}~cm & \num{10}x\num{10}x\num{10}~cm \\ \colhline
Top field cage penetrations (alternative design) & to achieve desired laser coverage & \\ \colhline
Data volume per 10~kton & 184 TB/year & 368 TB/year \\ \colhline
Longevity, internal parts	& \dunelifetime		& > \dunelifetime   \\    \colhline     
Longevity, external parts	& 5 years			& > \dunelifetime   \\ \colhline 
\textbf{Laser Beam Location System} & & \\ \colhline  
Laser beam location precision & 0.5~mrad & 0.5~mrad \\ \colhline
Longevity	& \dunelifetime		& > \dunelifetime   \\    \colhline     
\textbf{Photoelectron Laser System}	   &   &  \\ \colhline       Longevity, internal parts	& \dunelifetime		& > \dunelifetime   \\    \colhline 
Longevity, external parts	& 5 years			& > \dunelifetime   \\ \colhline 
\textbf{Pulsed Neutron Source System}	   &   &  \\ \colhline        
Coverage & > 75\% & 100\% \\ \colhline
Data volume per 10~kton & 144~TB/year & 288~TB/year
%DAQ rate per 10~kton & 190~TB/year & 168~TB/year
\\ \colhline 
Longevity	& 3 years			& > \dunelifetime   \\
\end{dunetable}
