%\section{Schedule and Milestones}


\begin{dunetable}
[Calibration consortium schedule]
{p{0.65\textwidth}p{0.25\textwidth}}
{tab:calib-sched}
{Key calibration construction schedule milestones leading to commissioning the first \dword{fd} module. (*) Schedule items related to the \dlong{rsds} (\dshort{rsds}) are to be considered pending system approval.}   
Milestone & Date (Month YYYY)   \\ \toprowrule
Laser systems design decision (including ionization, beam location and photoelectron systems) & January 2020 \\ \colhline 
Laser systems design review & February 2020 \\ \colhline 
\dword{pns} design decision  & March 2020 \\ \colhline
\dword{pns} design review & April 2020 \\ \colhline
\dword{rsds} design review & May 2020 \\ \colhline
Start of module 0 component production for ProtoDUNE-II & April 2020      \\ \colhline
End of module 0 component production for ProtoDUNE-II &  February 2021    \\ \colhline
\rowcolor{dunepeach} Start of \dword{pdsp}-II installation& \startpduneiispinstall      \\ \colhline
\rowcolor{dunepeach} Start of \dword{pddp}-II installation& \startpduneiidpinstall      \\ \colhline
 %\dword{prr} dates &      \\ \colhline
 \dword{prr} dates &   March 2022   \\ \colhline
\rowcolor{dunepeach}South Dakota Logistics Warehouse available& \sdlwavailable      \\ \colhline
\dword{rsds} demonstration test at ProtoDUNE-SP-II (*) &   April 2022   \\ \colhline
Start of  Laser and \dword{pns} production  &   May 2022   \\ \colhline
\rowcolor{dunepeach}Beneficial occupancy of cavern 1 and \dword{cuc}& \cucbenocc      \\ \colhline
End of \dword{pns} production & March 2023 \\ \colhline 
End of Laser system production  & July 2023     \\ \colhline
End of \dword{rsds} production (*) & August 2023     \\ \colhline
\rowcolor{dunepeach} \dword{cuc} counting room accessible& \accesscuccountrm      \\ \colhline
Start assembly of calibration production units in the cavern & May 2023\\ \colhline
\rowcolor{dunepeach}Top of \dword{detmodule} \#1 cryostat accessible& \accesstopfirstcryo      \\ \colhline
Start installation and alignment of Laser boxes & May 2024 \\ \colhline 
%End of  (component 1) production  &      \\ \colhline
%... & ...                       \\ \colhline
\rowcolor{dunepeach}Start of \dword{detmodule} \#1 TPC installation& \startfirsttpcinstall      \\ \colhline
Start installation of Laser System periscopes & August 2024 \\ \colhline 
Start installation of \dword{rsds} guide system (*) & August 2024 \\ \colhline 
\rowcolor{dunepeach}End of \dword{detmodule} \#1 TPC installation& \firsttpcinstallend      \\ \colhline
Installation of \dword{rsds} purge-boxes (*) & May 2025 \\ \colhline 
Installation of the \dword{pns} main components & June 2025 \\ \colhline
\rowcolor{dunepeach}Top of \dword{detmodule} \#2 accessible& \accesstopsecondcryo      \\ \colhline
 \rowcolor{dunepeach}Start of \dword{detmodule} \#2 TPC installation& \startsecondtpcinstall      \\ \colhline
\rowcolor{dunepeach}End of \dword{detmodule} \#2 TPC installation& \secondtpcinstallend      \\ 
\end{dunetable}

Table~\ref{tab:calib-sched} shows the schedule and key milestones for the calibration consortium that lead to commissioning the first \dword{fd} module. The demonstration of calibration systems design, operation, and performance at the \dword{pdsp}-II running is a key part of calibration schedule; those milestones are also listed in the table. The technology design decisions on calibration subsystems should be made by January 2020 for the laser system and by March 2020 for the neutron source system followed by technical design reviews. The production of design prototypes to be deployed at \dword{pdsp}-II running should be finished by February 2021 followed by assembly and deployment in \dword{pdsp} in March 2021. The \dlong{rsds} (\dshort{rsds})

design will follow a demonstration R\&D program outlined in detail in Table~\ref{tab:calib-rsds-sched} in the Appendix, with major milestones highlighted in this section. The major steps for systems approval are the design review in May 2020 and the deployment test at \dword{pdsp}-II in April 2022. 

Production of calibration systems for the \dword{fd} should start in March 2022, followed by assembly of the systems underground once the detector cavern becomes available in early 2023. Installing the laser system can begin as soon as the cryostat roof is accessible and conclude once the \dword{tpc} is ready to install. If it is approved, the \dword{rsds} guide system can begin installation just before\dword{tpc} is installed. The purge-boxes on top of the cryostat can be done later.
Installing the main components of the \dword{pns} will begin once the human access ports are no longer needed for \dword{tpc} installation in June 2025. 
