\chapter{Executive Summary}
\label{vl:tc-execsum}


The \dword{dune} \dword{tc} holds general responsibility for
facilities and functions related to the design, construction,
installation, and operation of the DUNE experiment as a whole. These
include all interfaces to \fnal, the host laboratory; to the
\dword{lbnf} at the \dword{surf} that houses and supports the
\dword{dune} detectors; to other surface facilities at or near \surf
operated for installation and operations activities; and to certain
other common test facilities operated for the benefit of
\dword{dune}. Led by the \dword{dune} \dword{tc}, \dword{dune}
\dword{tc} provides oversight and organizational support to the
consortia building the \dword{dune} detector.  This includes project
functions such as requirements, budget, scheduling, risk management,
value engineering, interface to national project management and
reporting. The \dword{tc} organization includes the lead
mechanical and electrical engineers for the experiment, who establish
and maintain standards and tools for all drawings and schematics, for
grounding and shielding, and for all DUNE subsystem-to-subsystem and
\dword{dune}-to-\dword{lbnf} interfaces. Other key member of
\dword{tc} include the \dword{dune} safety manager and the
\dword{dune} \dword{qa} manager. \dword{dune} \dword{tc} manages
the design, production and operational readiness reviews.

Chapters that follow lay out the structure of \dword{dune}
\dword{tcoord}, describe \dword{dune} facilities and detail
project-related functions and methodologies. At the stage of this
early draft to LBNC, \dword{dune} \dword{tc} has been most fully
developed for the \dword{dsp} detector. The volume will be expanded to
encompass all functions associated with both \dword{dsp} and
\dword{ddp} by the final draft.

