\chapter{Integration}
\label{vl:tc-integration}

[Farshid/Terri]

\section{Models}

In this section, integration models are explained: purpose, interfaces between them, methods of revision, methods of dissemination. [Farshid]
\begin{itemize}
 \item Static: method for control of fit for detector elements
 \item Installation envelopes: Method for control of fit during installation and operation
\end{itemize}

\begin{enumerate}
 \item A graphic showing each integration model nodes
 \item Graphics showing the interfaces between nodes
 \item Graphics showing detector interior views with dimensions
 \item Graphics showing the methods for controlling detector element dimensions, envelope dimensions and refence points (may need specific example)
 \item Graphics explaining the concept of, installation gaps, installation tolerances in the warm state
 \item Graphics showing concepts for alignment of detector elements
 \item Graphics showing effects of cold vs warm and control
 \item A set of figures showing the detectors inside the cryostat (SP and DP), clearances, service floor, cryogenic pipes, etc.
 \item Isometric view of cryostat in the caverns
 \item East-west and north side elevation views of cryostat in cavern identifying interfaces with LBNF
 \item Elevation views of top of detector, mezzanines, cryogenics, racks, etc. identifying interfaces with LBNF
 \item Detail drawings of interfaces: DSS to CS, feedthrough locations, CS opening, rack placement, grounding, cable trays, cooling interfaces, power interfaces, alignment interfaces.
 \item Detail drawings of interfaces: APA-HV, CE-APA, PD-APA
\end{enumerate}

\section{Drawings}

Plan for and methods of drawing storage, revisions and
dissemination. These are done by consortia for their drawings and by
TC for their drawings and for the interface and integration
drawings. [Farshid]

\section{Integration Drawings}

This section shows all interfaces. Many 2-d drawings will be needed
with dimensions and explanation. It will include all the interfaces
between systems, e.g. DSS to APA, APA to CE etc. [Farshid]

\section{Electrical Drawings}

plan for drawings and schematics showing connectors, pin outs, one
line power drawings etc. [Terri] (firmware, software)



\section{Electrical Integration Drawings}

shows all interfaces [Terri]

\section{Survey and ALignment}

this section will include methods of survey and alignment during
installation and maintenance during filling and operation. [Farshid]

\section{Interface Documents}

[Farshid/Terri] consortia-consortia, TC-consortia, TC-LBNF



