\chapter{Anne's Test}
\begin{dunetable}
[Installation System Risk Summary -Anne's test]
{p{0.05\textwidth}p{0.4\textwidth}p{0.4\textwidth}}
{tab:INSTALLrisks-anne}
{Installation Risk Summary}   
ID & Risk  & Mitigation\\ \toprowrule

1 & 
Work underground, work at heights, handling heavy equipment, tests with \dword{hv}, laser operation, and  other hazards can lead to personal injury.
& Follow FNAL safety program: procedures for work, training, use of \dword{ppe}, with levels of oversight. Use all reasonable measures to prevent workplace incidents. Still consider residual risk as critical.\\ \colhline
2 & 
Shipping delays can lead to installation delays. &
Plan one month buffer to store  materials locally.\\ \colhline
3 & 
Unavailability of components can delay assembly and installation. &
Use a detailed inventory system to verify availability of  necessary components prior to transport underground.\\ \colhline
4& 
Unavailability of international contract labor or equipment  can delay or prevent necessary work. &
Dedicated \dword{fnal} division in SD will expedite  import/export and visa related issues.\\ \colhline
5&
Limited availability of local trained workers can delay or prevent necessary work.
& Begin hiring process early; allow time for substantial training. Use Ash River installation prototype to train crew and optimize procedures.\\ \colhline
6&
Mismatch in dimensions or run-out in tolerances can lead to mechanical interferences. & 
Generate integration model of full \dword{detmodule}. Include key dimensions in integration drawings to control  interfaces.  Prototype assembly steps. Perform acceptance tests.\\ \colhline
7&
Human error in transport of heavy objects and work at heights with tools can lead to cryostat damage. & 
Construct false floor inside the cryostat for use during installation. Remove it as late as possible in process. Install temporary protection for work after its removal.\\ \colhline
8& 
Several times per year \dword{surf} closes for 1-2 days due to snow; closures can cause delays. & Include the average number of snow days in schedule.\\ \colhline
9&
Installation and cooling of components produces stress that can cause equipment failures.&
Test all components prior to delivery to SD to eliminate infant mortality failures. Cold test \dword{apa} assemblies once cabling and assembly is complete. Read out detector continuously to detect failures.\\ 
\end{dunetable}